Nitrogen cycling in the CLM5: controls on responses to environmental forcing

### 2018-06-29 main.tex
Updates from ShareLaTeX

2. \textbf{Impact of Ncosts}
Most of the variables and sites displayed a complex relationship between the Nitrogen costs and the response to CO$_{2}$ and N addition. 
For the tropical sites, where default N limitation is low and responses to Ndep are smaller, the simulations with a higher cost of N uptake push the system into a space where N expenditure is higher and so the response to fertilization is more pronounced. Conversely, for all sites, decreasing the cost of N

In general, the simulation with very high N uptake costs (large brown symbols) showed higher responses to N addition than the default case, on account of their large percentage expenditures on

whereas their response to CO$_{2}$ addition was not systematically different from the default.

>>>>

2. \textbf{Impact of Ncosts}
Most of the variables and sites displayed a complex relationship between the Nitrogen costs and the response to CO$_{2}$ and N addition. 
For the tropical sites, where default N limitation is low and responses to Ndep are smaller, the simulations with a higher cost of N uptake push the system into a space where N expenditure is higher and so the response to fertilization is more pronounced. Conversely, for all sites, decreasing the cost of N uptake increase Leaf Area Index
